Adaptive Algorithms Employing Continuous Linear Functionals

### 2018-08-03 AutoAlgorithmLinearFunctionalDataVerC.tex
revising "solvable"

Note that our problem is not solvable for $\cf$.  This can be proven by contradiction. We show that there is some function, $f \in \cf$, that looks like the zero function, but whose corresponding solution, $S(f)$, is far from $0$.   Choose any $A \in \ca(\cf)$ and $\varepsilon > 0$, and let $L_1, \ldots, L_n$ be the linear functionals are used to compute $A(0,\varepsilon)$. Since only a finite number of samples is used, there exists some nonzero $f \in \cf$ that  appears exactly like $0$ to the algorithm, but which has a non-zero solution, $S(f)$. This means that $L_1(f) = \cdots = L_n(f) = 0$, and so $A(cf,\varepsilon) = A(0,\varepsilon)$ for any real $c$.  Since our algorithm successfully produces an approximation with error no greater than $\varepsilon$,
\begin{align*}
    \varepsilon &\ge \frac 12 \left[ \norm[\cg]{S(0) - A(0,\varepsilon)} + \norm[\cg]{S(cf) - A(cf,\varepsilon)}\right] \\
    & =  \frac 12 \left[ \norm[\cg]{0 - A(0,\varepsilon)} + \norm[\cg]{S(cf) - A(0,\varepsilon)}\right] \\
    & \ge  \frac {\abs{c}\norm[\cg]{S(f)}}2  \qquad \text{by the triangle inequality}.
\end{align*}
Since $S(f) \ne 0$, it is impossible for this inequality to hold for all real $c$.  Thus, $\ca(\cf)$ is empty, and our problem is not solvable for $\cf$.  However, it is solvable for well-chosen subsets of $\cf$.

>>>>

Our problem is not solvable for $\cf$, as can be demonstrated by contradiction. For any potential algorithm, we show that there is some $f \in \cf$, that looks like $0$ to the algorithm, but for which $S(f)$ is far from $S(0) = 0$.   Choose any $A \in \ca(\cf)$ and $\varepsilon > 0$, and let $L_1, \ldots, L_n$ be the linear functionals are used to compute $A(0,\varepsilon)$. Since $n$ is finite, there exists some nonzero $f \in \cf$ satisfying that $L_1(f) = \cdots = L_n(f) = 0$ with non-zero $S(f)$. This means that $A(cf,\varepsilon) = A(0,\varepsilon)$ for any real $c$.  Since $A$ successfully produces an approximation with error no greater than $\varepsilon$ for both $0$ and $cf$,
\begin{align*}
    \varepsilon &\ge \frac 12 \left[ \norm[\cg]{S(0) - A(0,\varepsilon)} + \norm[\cg]{S(cf) - A(cf,\varepsilon)}\right] \\
    & =  \frac 12 \left[ \norm[\cg]{0 - A(0,\varepsilon)} + \norm[\cg]{S(cf) - A(0,\varepsilon)}\right] \\
    & \ge  \frac {\abs{c}\norm[\cg]{S(f)}}2  \qquad \text{by the triangle inequality}.
\end{align*}
Since $S(f) \ne 0$, it is impossible for this inequality to hold for all real $c$.  Thus, $\ca(\cf)$ is empty, and our problem is not solvable for $\cf$.  However, it is solvable for well-chosen subsets of $\cf$.
